---
title: "Cars Predicted value"
author: 'Prats Jamison '
date: '`r Sys.Date()`'
---
install.packages(knitr)
library(knitr)
```{r setup, include=FALSE}
library(knitr)
library(tufte)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(cache.extra = packageVersion("tufte"), tidy = FALSE)
options(htmltools.dir.version = FALSE)

```

## Calculating with R
Before we start we will load necessary libraries
```{R}
library(knitr)
library(leaps)#Exhaustive search for the best of variables in x for predicting y
library(e1071)#skewness and kurotosis
library(moments)
library(broom)
library(dplyr)
library(plyr)
library(ISLR)
library(plm)
library(lattice)
library(ggplot2)
```
To run the analysis , we need to load the data in to R
```{R}
#Read Data
Toyotacor <- read.csv("ToyotaCorolla.csv")
attach(Toyotacor)
summary(Toyotacor)
```

### Familiarize yourself with th data

```{R}
# Variable definition 
# MPG - Miles per galon 
# GPM - Galons per miles 
# WT - Weight 
# DIS - Dicplacement 
# NC - Number of cylinders 
# HP - Horsepower 
# ACC - acceleration (0-60mph) in seconds 
# ET - V-type engine (0) or straight (1) 

head(Toyotacor)

 # Become familiar with the data 
plot(Price ~ KM, data = Toyotacor)
plot(Price ~ Age, data = Toyotacor)
plot(Price ~ FuelType, data = Toyotacor)
plot(Price ~ HP, data = Toyotacor)
plot(Price ~ MetColor, data = Toyotacor)
plot(Price ~ Automatic, data = Toyotacor)
plot(Price ~ CC, data = Toyotacor)
plot(Price ~ Doors, data = Toyotacor)
plot(Price ~ Weight, data = Toyotacor)
```
### Prepare for analysis

Descriptive statistics are statistics that quantitatively describe or summarise features of a collection of information
```{R, eval=FALSE, include=FALSE}
#1.Descriptive Statistics
DS <- stat.desc(Toyotacor)
print(DS)
```

## Linear Regression 

Linear regression models are probably the most common used technique in data and buisiness analytics. They can be very powerful but one has to remember their limitations and constrains. The most important limitation is, that they should only be used to predict values within the range of the test data set. 
Here are are predicting the values for Toyota Coralla.

```{R}
options(max.print = 10)
# show results of first Analysis
Toyotacor.m1 <- lm(Price ~ ., data = Toyotacor)
summary(Toyotacor.m1) # Show results of the first model
#Confident Interval
confint(Toyotacor.m1)
Toyotacor.m1.confint <- confint(Toyotacor.m1)
## Check with a correlation matrix if predictor variables are themselves related
Toyotacor.D= as.data.frame(matrix(Toyotacor))[1,]
TyCo.col <- cor(data.frame(lapply(Toyotacor.D, rank)))
head(print(TyCo.col))
```

# Calculate regression - Model 1
```{R}
options(max.print = 10)
#calculate regression - Model 1
x <- Toyotacor[, 2:10] # independent variable
head(x)
y <- Toyotacor[,1] # dependent variable
head(y)
#model selection 
Toyotacor.out <- summary(regsubsets(x,y, nbest = 2, nvmax = ncol(x)))
Toyotacor.regtab <- cbind(Toyotacor.out$which, Toyotacor.out$rsq, Toyotacor.out$adjr2, Toyotacor.out$cp)

colnames(Toyotacor.regtab) <- c("(Intercept)", "Age", "KM", "FuelType", "HP", "MetColor", "Transmission", "CC" , "Doors", "Weight", "R-Sq", "R-Sq(adj)", "Cp")
print(Toyotacor.regtab) # pValue is < 0.05, so we reject null hypothesis
head.matrix(Toyotacor.regtab)
```

### Regression analysis with the given variable 7 expect km and windows and also find the car cost using these variables

```{r} 
options(max.print = 10)
#create second model 
Toyotacor.m2 <- lm(Price~ Age + FuelType+HP+MetColor+ Automatic+ CC + Doors, data = Toyotacor) #just with weight
Toyotacor.m2.summary <- summary(Toyotacor.m2)
head(print(Toyotacor.m2.summary))


#Model 2 Conf Intervals
Toyotacor.m2.confint <- confint(Toyotacor.m2)
head(print(Toyotacor.m2.confint))

Toyotacor.m2 <- lm(Price~ Age + FuelType+HP+MetColor+ Automatic+ CC + Doors, data = Toyotacor)
head(Toyotacor.m2)

#Assigning values
given.Toyotacor <- data.frame(Age=12, FuelType=1, HP=185, MetColor=1, Automatic=0, CC=2000, Doors=4)
predicted.price <- predict(Toyotacor.m2,given.Toyotacor)
as.data.frame(print(predicted.price))# Predicted Car Value
```

```{R}
options(max.print = 10)
#predicted Values/ Residuals
Toyotaco_hat <- fitted(Toyotacor.m1)# predicted values
print(Toyotaco_hat)
Toyota_resid <- residuals(Toyotacor.m1) # residuals
print(Toyota_resid)
```
## So now that we have two models, the question would be, which one is better? In order to answer this question, we need to cross validated the combinaion of each model. let us start with the first model.
### cross- validation ( leave one out) for the model on all six regressors

```{R}
options(max.print = 10)
n <- length(Toyotacor$Price)
diff <- dim(n)
percdiff <- dim(n)
for (k in 1:n) {
  train1 <- c(1:n)
  train <- train1[train1 !=k ]
  m2 <- lm(Price~ ., data = Toyotacor[train,])
  pred <- predict(m2, newdat = Toyotacor[-train,])
  obs <- Toyotacor$Price[-train]
  diff[k] <- obs - pred
  percdiff[k] <- abs(diff[k]) / obs
}
Toyotacor.m2.me <- mean(diff)
Toyotacor.m2.rmse <- sqrt(mean(diff**2))
Toyotacor.m2.mape <- 100*(mean(percdiff))

Toyotacor.m2.me
Toyotacor.m2.rmse
Toyotacor.m2.mape
predicted.price
```

```{R}
#check if assumptions are met...
plot(Toyotacor.m1)
ggsave("HW3 Graph/ToyotaCorlin.pdf")
```

