---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

---
title: "ER Waiting"
author: "Prats Jamison"
date: "October 28, 2016"
output: 
  pdf_document: 
    keep_tex: yes
    number_sections: yes
    toc: yes
---

library(sqldf)
library(caret)
library(ROCR)
library(car)
library(effects)
library(colorspace)
library(lattice)
library(grid)
library(foreign)
library(readr)
library(dplyr)
library(knitr)


turnover = read.csv("ERWaiting.csv")
---

#Introduction : 
This is the HW assignment for week 2 date (10/15). Here were are analysing the ER waiting time by calculating descriptive statistice, Anova, and graphs.

## Descriptive Statistics
Descriptive statistics are numbers that are used to summarize and describe data. The word "data" refers to the information that has been collected from an experiment, a survey, a historical record, etc.

```{r, eval=FALSE}
summary(ERWaiting)
stat.desc(ERWaiting)
qqnorm(ERWaiting$waitingTime)
qqline(ERWaiting$waitingTime)
```
### Anova
Analysis of Variance(ANOVA) is a collecition of statitical models used ti analyze the difference amoung group means and thier associated procedures ( such as "variation" among and between groups). 

In our ANOVA analysis our P value is < 0.05, so we can reject the null hypotesis and from the Tukey polt we can see that Main has the highest mean and satelite 1 has the lowest mean. 


```{r}
fit <- lm(data = ERWaiting, waitingTime~hospital)
ERWaiting.aov <- aov(fit)
ERWaiting.aov.summary <- summary(ERWaiting.aov)
ERWaiting.tukey <- TukeyHSD(ERWaiting.aov)
plot(ERWaiting.tukey)
ERWaiting.normal <- data.frame(skew = ERWaiting$skew, kurt = ERWaiting$kurtosis)
ERWaiting.levene <- leveneTest(fit)
df <- anova(fit)[, "Df"]
names(df) <- c("between", "within")
ERWaiting.f.crit <- qf(alpha, df["between"], df["within"], lower.tail = FALSE)
ERWaiting.f.value <- ERWaiting.aov.summary[[1]]$F[1]
ST <- shapiro.test(ERWaiting$waitingTime)
ST
SC <- plot(ERWaiting$hospital)
SC
HS <- hist(ERWaiting$waitingTime)
HS
bp <- ggplot(ERWaiting, aes(x = hospital, y = waitingTime)) +
  geom_boxplot() + 
  labs(y = "Average Waiting Time", x = "Hospitals") 
bp
```

``` {r, echo=FALSE}
kable(ERWaiting)
```


